Visualizations for the manuscript

### 2022-05-17 metanalysis_visualization/manuscript_Figures.Rmd
chisq test for disorder group table 1

>>>>

### estimate thhe pvalue for the diosrder groups (chi.sq test)
disorder_group_table_all <- table1_all %>%
  filter( Category == "Disorder groups" & name != "Total") %>%
  mutate( before_counts = sapply(strsplit( before_pandemic, " "), '[', 1), 
          during_counts = sapply(strsplit( during_pandemic, " "), '[', 1)) %>%
  group_by( name ) %>%
  summarise( before_pandemic_yes = sum( as.numeric( before_counts ), na.rm = TRUE), 
             during_pandemic_yes = sum( as.numeric( during_counts ), na.rm = TRUE), 
             before_pandemic_no  = 9696-before_pandemic_yes, 
             during_pandemic_no = 10561- during_pandemic_yes , 
             p_value = chisq.test( matrix( c(before_pandemic_yes, during_pandemic_yes, before_pandemic_no,  during_pandemic_no), ncol = 2, nrow = 2))$p.value, 
             p_value_formated = format.pval(p_value, digits=3, eps=0.001))

p_value_breaks = c(-Inf, 0, 0.0001, 0.001, 0.01, 0.05, Inf)
p_value_labels = c("", "****", "***", "**", "*", "")

setDT(disorder_group_table_all)[, PVAL := cut(p_value,
                                 breaks = p_value_breaks,
                                 right = FALSE,
                                 labels = p_value_labels)]
#####
